Towards a framework for reasoning about stateful compiler IRs using coinductive reasoning.

### 2024-06-25 paper.tex
fix quotes

I'm planning to write a paper about this work tentatively titled: "\emph{Taming the Bitvector Bestiary: A Characterization of Whitebox Bitvector Proof Strategies}", 
in which we explore all of these different strategies, 
classify exactly which class of expressions they solve, 
and investigate how many real-world problems are already covered by these strategies.
The aim is to submit this to PLDI, which has its call for papers around November.

>>>>

I'm planning to write a paper about this work tentatively titled: ``\emph{Taming the Bitvector Bestiary: A Characterization of Whitebox Bitvector Proof Strategies}'', 
in which we explore all of these different strategies, 
classify exactly which class of expressions they solve, 
and investigate how many real-world problems are already covered by these strategies.
The aim is to submit this to PLDI, which has its call for papers around November.
